Comparison of WAIS accumulation trends in PAIPR to RACMO

### 2022-05-27 notebooks/compare-racmo.Rmd
Adds notebook for testing spacetime modeling examples with Kronecker sums for effects

ggplot(dat.gdf) + 
  geom_sf(aes(color=trend.res))  + 
  # scale_color_gradientn(colours = cet_pal(7, name = "d1"))
  scale_color_gradient2()
```

>>>>

ggplot(dat.gdf) + 
  geom_sf(aes(color=estimate.accum))  + 
  # scale_color_gradientn(colours = cet_pal(7, name = "d1"))
  scale_color_gradient2()

ggplot(dat.gdf) + 
  geom_sf(aes(color=trend.res))  + 
  # scale_color_gradientn(colours = cet_pal(7, name = "d1"))
  scale_color_gradient2(limits=c(-0.025, 0.005))
```
